### 2022-07-07 paper/Chapters/Chapter05.tex
update evaluation

%% nnnn exp
\section{Surface Normal Inference based on Depth Map}
The goal of surface normal inference is to calculate the tangent surface normal map $ N $ from a single depth map $ D $. A network named Gated Convolution Neural Network (GCNN) is trained and is compared with similar approaches.

\subsection{Compared Approaches}

\subsection{Training Details}
The network (see \ref{gcnn}) is trained on stated dataset in Chapter \ref{ch:04}. It has two versions, the L-size $ 512\times512\times3 $ and the  S-size $ 128\times128\times3 $. For the L-size model, it uses batch size 8 for 3500 iterations. For the S-size model, it uses batch size 32 for 6000 iterations. Both sizes use Adam optimizer \cite{adam} with a learning rate of $ 1\times10^{-3} $, penalty-l2 loss(see \ref{sec:loss}). The output is directly the tangent normal in range $ \left[-1,1\right] $. The output and input has the same shape.

@@

The evaluation visualization on dataset ``synthetic50-5" (see \ref{ch:04}) dataset is shown in Figure \ref{fig:gcnn-eval-synthetic}. It compares the results with method xxx, for both smooth and highly detailed cases. In all the cases, the angle errors are very close. The test-cases are based on test point cloud in ``synthetic50-5".

The model is supposed to used on any image size since it has no fully-connected layers (dense layers). Two size of models are based on exactly the same architecture.

@@

The evaluation visualization on real dataset is shown in Figure \ref{fig:gcnn-eval-real}
\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_point_cloud_noise.png}
		\caption{point cloud}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_groundtruth.png}
		\caption{ground-truth}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_normal_GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_error_GCNN.png}
		\caption{Angle Error}
	\end{subfigure}
	\caption{Evaluation on Real Dataset}
	\label{fig:gcnn-eval-real}
\end{figure}

>>>>

%% nnnn exp
\section{Surface Normal Inference based on Depth Map}
The goal of surface normal inference is to calculate the tangent surface normal map $ N $ from a single depth map $ D $. A network named Gated Convolution Neural Network (GCNN) ( \ref{gcnn}) is trained and is compared with similar approaches. We evaluate the performance of the model in dataset ``synthetic50-5" introduced in  \ref{ch:04} including 5K depth maps with size  $ 512\times512\times3 $ for training. All the depth maps add simulated noise as introduced in \ref{sec:noise}. The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, penalty-l2 loss(see \ref{sec:loss}). The output is directly the tangent normal in range $ \left[-1,1\right] $. The output and input has the same shape.

@@

The visual evaluation on model GCNN shown in Figure \ref{fig:gcnn-eval-synthetic-full}.

@@

The evaluation visualization on test dataset is shown in Figure \ref{fig:gcnn-eval-synthetic}. Figure \ref{fig:gcnn-eval-synthetic-zoom-in} zooms in the hindhead area of the dragon object which provides a closer comparison with the ground-truth.
\begin{figure}[th]
	\centering
	\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_input.png}
		\caption{Input}
	\end{subfigure}
	\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_GT.png}
		\caption{GT}
	\end{subfigure}
		\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_GCNN.png}
		\caption{GCNN}
	\end{subfigure}
		\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_SVD.png}
		\caption{SVD}
	\end{subfigure}
	\begin{subfigure}[b]{0.15\linewidth}
	\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_error_GCNN.png}
	\caption{}
	\end{subfigure}
	\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_error_SVD.png}
		\caption{}
	\end{subfigure}
	\caption{Zoom in of dragon object evaluation.}
	\label{fig:gcnn-eval-synthetic-zoom-in}
\end{figure}

The evaluation visualization on real dataset is shown in Figure \ref{fig:gcnn-eval-real}
\begin{figure}[th]
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_point_cloud_noise.png}
		\caption{point cloud}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_groundtruth.png}
		\caption{ground-truth}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_normal_GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_error_GCNN.png}
		\caption{Angle Error}
	\end{subfigure}
	\caption{Evaluation on Real Dataset}
	\label{fig:gcnn-eval-real}
\end{figure}
